Deep Reinforcement Learning for Conservation Decisions

### 2021-06-04 manuscript/manuscript.Rmd
First pass

One feature that most distinguishes deep RL from other approaches to decision theory (such as optimal control) is its flexibility and scope.
While optimal control approaches typically require extensive simplifying assumptions such as discrete states or actions, deterministic dynamics or short time horizons, deep RL is scoped more ambitiously.
Large, complex problems are still challenging to RL, and existing RL approaches can easily struggle to solve problems that can already be solved much more efficiently by other means.
Nevertheless, deep RL approaches have proven successful on problems that classical approaches could not solve despite immense computational resources -- e.g. deep RL  [@DQN, @alphago].
Our previous examples have focused on relatively simple problems that can also be addressed at least approximately by conventional methods, and also permit RL-based solutions to be found relatively efficiently on commodity hardware.
Yet, we also have developed

>>>>

The feature that most distinguishes deep RL from other approaches to decision theory (such as optimal control) is its scope.
While optimal control approaches typically require extensive simplifying assumptions such as discrete states or actions, deterministic dynamics or short time horizons, deep RL can work on a much broader range of problems.
Deep RL algorithms have proven successful on a range of problems that classical approaches could not solve despite immense computational resources -- e.g. deep RL can solve control problems with image-based observations that would be intractable with classical methods [@DQN]--; yet, getting deep RL to work in practice can be unexpectedly challenging and computationally intensive.
Our previous examples have thus focused on relatively simple problems that can be addressed by conventional methods, and also permit RL-based solutions to be found relatively efficiently on commodity hardware.
We have developed more conservation-based RL environments that range in difficulty to solve; an active list of these environments can be found at <https://boettiger-lab.github.io/conservation-gym/>.
